The population of long-period exoplanets --- \\ Fully-automated discovery \& characterization of long-period transiting exoplanet candidates in the \kepler\ archive \vspace{-3\baselineskip}

### 2016-06-29 document/ms.tex
not much

To evaluate \eq{gpmeangrad}, we must also evaluate the derivative of the mean
model with respect to its parameters.
For this \paper, the model $m(\bvec{t};\,\meanpars)$ will sometimes be the
limb-darkened, exposure time-integrated transit of a planet on a Keplerian
orbit and the parameters \meanpars\ are the physical and orbital parameters of
the planet and star.
Analytically computing the gradient of a simple transit model is possible
\citep{Pal:2008} but it becomes substantially more tedious as the model
becomes more realistic.
Therefore, we use a compile-time automatic differentiation library\footnote{%
More specifically, we use the \texttt{Jet} object from the BSD-licensed Ceres
Solver \url{http://ceres-solver.org}} \citep{Agarwal:2016} to compute first
derivatives of the full transit model to machine precision.

>>>>

To evaluate \eq{gpmeangrad}, we must also evaluate the derivative of the mean
model with respect to its parameters.
